PRIMUS: Quiescent Fraction as a Function of Environment and Redshift

### 2014-05-24 qfenv_paper/qf_environment.tex
clashing?

\subsection{Target Galaxy Sample} \label{sec:target} 
In this section we will define the target galaxy sample 
used to compute the SMFs and QFs. The population 
at $z \sim 0.5$ is derived from PRIMUS data and the 
population at $z \sim 0.1$ is derived from SDSS-{\em GALEX} 
data, both described above. For the intermediate redshift 
population, we begin with the selection criteria imposed 
in \cite{Moustakas:2013aa} for their parent sample. We 
take the statistically complete {\em primary} sample from 
the PRIMUS data (\cite{Coil:2011aa}) and impose magnitude 
limits on optical selection bands as specified in 
\cite{Moustakas:2013aa} Table 1. These limits are in different 
optical selection bands and have distinct values for the 
five PRIMUS target fields. We then exclude stars and 
broad-line AGN to only select objects spectroscopically 
classified as galaxies, with high-quality spectroscopic redshifts 
($Q \geq 3$) within the redshift range $0.2 - 0.8$. For 
each of these objects we assign statistical weights (described 
in \cite{Coil:2011aa} and \cite{Cool:2013aa}) in order to correct 
for targeting incompleteness and redshift failures. The 
statistical weight, $w_i$, for each galaxy is given by
\begin{equation}
w_{i} = (f_{\rm{target}} \times f_{\rm{collision}} \times f_{\rm{success}})^{-1},
\end{equation}
Equation (1) in \cite{Moustakas:2013aa}. Then to account 
for stellar mass incompleteness, we impose derived stellar 
mass limits to the sample.

Stellar mass completeness limits for a magnitude-limited 
survey such as PRIMUS is a function of redshift, apparent 
magnitude limit of the survey, and the typical stellar 
mass-to-light ratio of galaxies near the flux limit. As done 
in \cite{Moustakas:2013aa}, we follow \cite{Pozzetti:2010aa} 
to empirically determine the stellar mass completeness limits.
Briefly, for each of the target galaxies we compute 
$\mathcal{M}_{\rm{lim}}$ using $\rm{log} \; \mathcal{M}_{\rm{lim}} = \rm{log} \; \mathcal{M} + 0.4 ( m - m_{\rm{lim}})$.
$\mathcal{M}$ is the stellar mass of the galaxy in $\mathcal{M_{\odot}}$, 
$\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy 
if its magnitude was equal to the survey magnitude limit, 
$m$ is observed apparent magnitude in the selection band, 
and $m_{\rm{lim}}$ is the magnitude limit for our five 
fields mentioned above. We construct a cumulative 
distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ 
faintest galaxies in $\Delta z=0.04$ bins. In each of these 
redshift bins, we calculate the minimum stellar mass that 
includes $95 \%$ of the galaxies. Separately for quiescent 
and star-forming galaxies, we fit quadratic polynomials to 
the minimum stellar masses versus redshift (galaxies are 
classified into star-forming or quiescent in the following section).
Finally, we use the polynomials to obtain the minimum stellar 
masses at the center of redshift bins, $0.2-0.4$, $0.4-0.6$, 
and $0.6-0.8$, which are then used as PRIMUS stellar mass
completeness limits.

For our target galaxy population at low redshift we start with 
the SDSS-{\em GALEX} data. We limit our population within 
the redshift range $0.0375-0.145$ due to redshift limits later 
imposed on the volume-limited Environment Defining Population 
(Section \ref{sec:environment}). To account for targeting 
completeness of this sample, we use the statistical weight 
estimates provided by the NYU-VAGC. Then to account for 
stellar mass incompleteness, we impose a uniform stellar mass 
limit of $10^9.8 \mathcal{M}_{\odot}$, a limit determined by the 
stellar mass-to-light ratio completeness of the NYU-VAGC 
sample given the redshift limits.

The absolute magnitude ($M_{r}$) versus redshift for the 
target galaxy population (black squares) is plotted in Figure 
\ref{fig:targetEDP}. The left-most panel corresponds to the
target sample derived from the SDSS-{\em GALEX} data and
the rest correspond to the target sample derived from the 
PRIMUS data divided in bins with $\Delta z \sim 0.2$.

@@

\begin{figure*}
  \begin{center}
    \leavevmode
     \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_25_2envbin_primuszerr.eps,height=0.75\textwidth,angle=90}
     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) target galaxies in 
low (left) and high (right) environments from redshift range $z=0-0.8$. The environment of each galaxy  
was calculated using a cylindrical aperture size of $R=2 \: \rm{Mpc}$ and $H=25 \: \rm{Mpc}$ and  
classification based on the cut-offs specified in Table \ref{tab:aperture}. The SMFs use mass bins of 
width $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.25$. In each panel we use shades of blue 
(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
progressively lighter.}      \label{fig:smf}
    \end{center}
\end{figure*}

@@

For the SDSS-{\em GALEX} EDP (hereafter SDSS EDP), we do not use the parent data of 
the SDSS-{\em GALEX} target sample which uses the geometry of the combined angular selection function of the 
SDSS VAGC and {\em GALEX}. 
Instead, since FUV, NUV values are not necessary for EDP, we extend the parent data of the SDSS EDP
to the entire SDSS VAGC, including galaxies outside of the {\em GALEX} window function. 
Furthermore, we impose a redshift range of $0.0375-0.145$ on the SDSS EDP. 
This redshift range is due to the lack of faint galaxies at $z \sim 0.2$ and the lack of bright galaxies at 
$z \sim 0.01$ in the SDSS VAGC data.  
The lower bound for the redshift range was empirically determined by the bright limit and the upper bound 
by the faint limit of the $M_{r}$ versus redshift distribution. 
The same fixed cumulative number density method, described above, is used on this SDSS EDP to equate
the cumulative number density of SDSS EDP to the highest redshift bin of the PRIMUS EDP. 
Ultimately, we get $M_{r,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$ for the redshift bins $0.0375-0.145$, 
$0.2-0.4$, $0.4-0.6$, $0.6-0.8$, respectively.  %%%% PUT NEW VALUES
These absolute magnitude limits are illustrated in Figure \ref{fig:targetEDP}, which plots $M_{r}$ distribution as 
a function of redshift for the EDP (red) and the target galaxy sample (black).

@@

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_25_primuszerr.eps,height=0.75\textwidth,angle=90}
        \caption{Evolution of the quiescent fraction $f_{\rm{Q}}$ for target galaxies in spare (left) and dense (rights) environments
from $z \sim 0.7$ to $z \sim 0.1$. $f_{\rm{Q}}$s were calculated using the SMFs computed in Section \ref{sec:smf} and shown in Figure\ref{fig:smf}, as described in text. Darker shading indicates lower redshift.}         \label{fig:qf}
    \end{center}
\end{figure*}

@@

%\section{Results}
%In the section below, we calculate stellar mass functions (SMFs) for the target galaxy population divided into 
%quiescent/star-forming and dense/sparse environment, Section \ref{sec:smf_const}. We use a non-parametric 
%$1/V_{\rm{max}}$ estimate of SMFs for the subsamples further divided into redshift bins. Then using these 
%SMFs, we calculate the quiescent fractions (QFs), Section \ref{sec:qf_const}, 
%and examine it's evolution over our redshift range.

\section{Stellar Mass Function} \label{sec:smf}
The target galaxy sample defined above has so far
been classified into quiescent or star-forming and 
dense or sparse. We further divide these subsamples 
into bins of redshift:  in redshift bins of $0.0375-0.145$, 
$0.2-0.4$, $0.4-0.6$, and $0.6-0.8$. While the 
PRIMUS data ranges from $0.2 < z < 1.2$, we only 
consider galaxies with $ z<0.8$ due to insufficient
statistics for robust environment measurements at 
higher redshifts. With added redshift bins, we have a
total of 16 subsamples. We calculate the SMF for 
each of these 16 subsamples.

@@

In order to calculate the uncertainty of the SMFs from the sample 
variance, we use a standard jackknife technique as done in \cite{Moustakas:2013aa}.
For the PRIMUS target galaxies, we calculate SMFs after excluding 
one of the five target fields each time. And for the SDSS target galaxies
we divide the field into a 30 $\times$ 20 rectangular $RA$ and $Dec$ 
grid and calculate the SMFs after excluding part of the field each time. 
Then using the calculated SMFs we calculate the uncertainty: 
\begin{equation}
\sigma^j = \sqrt{\frac{M-1}{M} \sum\limits_{k=1}^{M} (\Phi^j_k - \langle \Phi^j \rangle)^2}
\end{equation} 
$M$ in this equation is the number of jack knife SMFs in the stellar mass
bins. $\langle \Phi^j \rangle$ is the mean number density of galaxies 
in each stellar mass bin for all of the jack knife $\Phi^j$s.

SMFs for 16 target galaxy subsamples classified into quiescent/star-forming (orange/blue)and 
dense/spare environments are presented in Figure \ref{fig:smf}. The 
redshift evolution of the SMFs are indicated by a darker shade for lower
redshifts. The sample variance uncertainties are represented by the 
width of the SMFs. The environment measurements and classifications
for Figure \ref{fig:smf} are done using a cylindrical aperture with dimensions,
$R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and $H_{\rm{ap}} = 25 \; \rm{Mpc}/h$.

Examining the SMF evolution from $z \sim 0.7$ to $z \sim 0.1$, 
we find that in dense environments both the star-forming and quiescent
SMFs increase at $\mathcal{M}_{*}$ below the knee of mass function 
($\rm{log}\: \mathcal{M}_{*}/\mathcal{M}_{\odot} < 10.75$ for star-forming; 
$\rm{log}\: \mathcal{M}_{*}/\mathcal{M}_{\odot} < 11.0$ for quiescent). 
Meanwhile, at masses above the knee the SMFs for dense environments 
exhibit little change throughout the redshift range.

At sparse environments, the quiescent SMF remains relatively constant 
for galaxies with $\rm{log}\: \mathcal{M}_{*}/\mathcal{M}_{\odot} < 10.75$.
At higher stellar masses, however, the SMF decreases notably. Finally 
the sparse environment star-forming SMF shows a decrease at all 
stellar mass ranges over the redshift range.

%%% COMPARISON TO OTHER LITERATURE?

\section{Quiescent Fraction} \label{sec:qf_const}
From the SMF number densities ($\Phi$) calculated
in the previous section, the quiescent fraction is computed 
as follows, 
\begin{equation}
f_{\rm{Q}} = \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
\end{equation}
$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies 
per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.25$ 
for the quiescent and star-forming subsamples, respectively 
(Equation \ref{eq:phi}). We compute $f_{\rm{Q}}$ for dense 
and spare environments over our redshift range as plotted in
 Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ 
 for dense (right) and sparse (left) environments. As in 
 Figure \ref{fig:smf}, the darker shading represent lower redshifts.

For both the spare and dense environments there is a notable 
increase in $f_{\rm{Q}}$ at all stellar masses as redshift decreases.
%%% INCLUDE BRIEF QUALITATIVE ANALYSIS OF THE EVOLUTION OF THE QUIESCENT FRACTION

@@

The figures and analysis described in this paper are done using galaxy environment determined from a fixed aperture with $r_{\rm{ap}} = 1 \rm{Mpc}$ and $h_{\rm{ap}} = 50 \rm{Mpc}$.
The same analysis was repeated for various aperture dimensions: $r_{\rm{ap}} = 0.5, 1, 2, 3 \rm{Mpc}$ and $h_{\rm{ap}} = 25, 50 \rm{Mpc}$. 
Minor adjustments to the environment classification thresholds were adopted in these analyses for the smaller apertures ($r_{\rm{ap}} = 0.5, 1 \rm{Mpc}$ and $r_{\rm{ap}} = 25 \rm{Mpc}$).
The results obtained from using these different are consistent with the results displayed in this paper. 
\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \plotone{fig_qffit_cylr2h25_thresh75_bin0_25.png}
        \label{fig:qffit}
        \caption{Quiescent fraction at fiducial mass $\rm{log} (\mathcal{M}/\mathcal{M}_{\odot}) = 10.5$ for 
low (square) and high (circle) environments in the redshift range $z = 0 - 0.8$. The evolution of 
$f_{Q}(\mathcal{M}_{\rm{fid}})$ for galaxies in different environments shows an evolution over the redshift
range that is independent of environment density. Futhermore throughout the redshift range the difference in 
$f_{Q}(\mathcal{M}_{\rm{fid}})$ remains relatively constant and $ < 0.15$.}
    \end{center}
\end{figure}

\section{Summary}
We have measured the SMFs and QFs using low redshift SDSS-{\em GALEX} galaxies and intermeidate redshift PRIMUS galaxies. 
Specifically we anlayzed the evolution of the QFs over the redshift range $0.0-1.0$ for galaxies in environment densities (Figure \ref{fig:qf}). 
We find that there is an expected increase in QF with decrease in the redshift for subsamples in all environment densities.
More importantly we find that the change in QF over redshift is independent of the environment and remains relatively equal for all environments.

@@

\subsection{Stellar Mass Function} \label{sec:smf_const}
\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \plotone{fig_smf_cylr1h25_thresh80_bin0_25.png}
        \caption{SMF for $r_{\rm{ap}}=1 \rm{Mpc}$ and $h_{\rm{ap}}=25 \rm{Mpc}$}
    \end{center}
\end{figure*}

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \plotone{fig_qf_cylr1h25_thresh80_bin0_25.png}
        \caption{QF for $r_{\rm{ap}}=1 \rm{Mpc}$ and $h_{\rm{ap}}=25 \rm{Mpc}$}
    \end{center}
\end{figure*}

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \plotone{fig_qffit_cylr1h25_thresh80_bin0_25.png}
        \caption{QF at fiducial mass for $r_{\rm{ap}}=2 \rm{Mpc}$ and $h_{\rm{ap}}=50 \rm{Mpc}$}
    \end{center}
\end{figure*}

>>>>

\subsection{Target Galaxy Sample} \label{sec:target} 
In this seciton we will define the target galaxy sample we use to compute the SMFs and QFs.
The population at $z \sim 0.5$ is derived from the PRIMUS data and the population at $z \sim 0.1$ is derived from the SDSS data, both described above.
For the intermediate redshift target galaxy population, we begin with the selection criteria imposed in \cite{Moustakas:2013aa} for its parent sample.
We take the statistically complete {\em primary} sample from the PRIMUS data (\cite{Coil:2011aa}) and then impose magnitude limits on optical selection bands as specified in 
\cite{Moustakas:2013aa} Table 1.
These limits are in different optical selection bands and have different values for our five PRIMUS target fields.
Next, we join the PRIMUS, {\em GALEX}, and IRAC window functions to construct the angular selection function.
We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$) within the 
redshift range $0.2 - 0.8$.
Afterwards we assign statistical weights (described in \cite{Coil:2011aa} and \cite{Cool:2013aa}) to the objects in order to correct for targeting incompleteness and redshift failures.
The statistical weight, $w_i$, for each galaxy is given by
\begin{equation}
w_{i} = (f_{\rm{target}} \times f_{\rm{collision}} \times f_{\rm{success}})^{-1},
\end{equation}
Equation (1) in \cite{Moustakas:2013aa}.
In addition to the selection criteria above, we impose stellar mass limits to have a stellar mass complete sample.  
Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS is a function of redshift, apparent magnitude limit of the survey, and the typical stellar 
mass-to-light ratio of galaxies near the flux limit.

As done in \cite{Moustakas:2013aa}, we follow \cite{Pozzetti:2010aa} to empirically determine the stellar mass completeness limits.
Briefly, for each of the target galaxies we compute $\mathcal{M}_{\rm{lim}}$ using $\rm{log} \; \mathcal{M}_{\rm{lim}} = \rm{log} \; \mathcal{M} + 0.4 ( m - m_{\rm{lim}})$.
$\mathcal{M}$ is the stellar mass of the galaxy in units of $\mathcal{M_{\odot}}$, $\mathcal{M}_{\rm{lim}}$ is the stellar mass of each galaxy if its magnitude was 
equal to the survey magnitude limit, $m$ is observed apparent magnitude in the selection band, and $m_{\rm{lim}}$ is the magnitude limit for our five fields mentioned above.
We construct a cumulative distribution of $\mathcal{M}_{\rm{lim}}$ for the $15\%$ faintested galaxies in $\Delta z=0.04$ redshift bins.
In each of these redshift bins, we calculate the minimum stellar mass that includes $95 \%$ of the galaxies.
Separately for quiescent and star-forming galaxies, we fit quadratic polynomials to the minimum stellar masses versus redshift (classificiation scheme for quiescent 
and star-forming galaxies is included in the following section).
Finally, we use the polynomials to obtain the minimum stellar masses at the center of the redshift bins, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, and $0.8-1.0$.
These redshift bins will later be used to divide the target sample in order to compute the SMFs and QFs.

For our target galaxy population at low redshift we use our SDSS-{\em GALEX} data. 
We limit our target population within the redshift range $0.0375-0.145$ due to redshift limits later imposed for the volume-limited Environment Defining Population (Section \ref{sec:environment}).
The NYU-VAGC provides statistical weight estimates for targeting completeness.
In order to have a stellar mass complete low redshift target population, we use a uniform stellar mass limit of $10^9 \mathcal{M}_{\odot}$, which is above the surface 
brightness and stellar mass-to-light ratio completness limits (\cite{Blanton:2005ab}; \cite{Baldry:2008aa}).
The absolute magnitude ($M_{r}$) versus redshift for the target galaxy population at both low redshift and intermediate redshift is plotted in Figure \ref{fig:targetEDP}.
For further details we refer readers to \cite{Moustakas:2013aa} for details; more specifically, Figure 2., Sections 3.1, and 4.3.

@@

\begin{figure*}
  \begin{center}
    \leavevmode
     \label{fig:smf}
     \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_25.eps,height=0.75\textwidth,angle=90}
     \caption{NEED TO UPDATE WITH CORRECT SDSS MASS LIMIT. Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) galaxies in 
low (left) and high (right) environments from redshift range $z=0-0.8$. The environment of each galaxy  
was calculated using a cylindrical aperture size of $R=2\rm{Mpc}$ and $H=25\rm{Mpc}$ and  
classification based on the cut-offs specified in Table \ref{tab:aperture}. The SMFs use mass bins of 
width $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.25$. In each panel we use shades of blue 
(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
progressively lighter.}
    \end{center}
\end{figure*}

@@

For the SDSS-{\em GALEX} EDP (hereafter SDSS EDP), we do not use the parent data of 
the SDSS-{\em GALEX} target sample which uses the geometry of the combined angular selection function of the 
SDSS VAGC and {\em GALEX}. 
Instead, since FUV, NUV values are not necessary for EDP, we extend the parent data of the SDSS EDP
to the entire SDSS VAGC, including galaxies outside of the {\em GALEX} window function. 
Furthermore, we impose a redshift range of $0.0375-0.145$ on the SDSS EDP. 
This redshift range is due to the lack of faint galaxies at $z \sim 0.2$ and the lack of bright galaxies at 
$z \sim 0.01$ in the SDSS VAGC data.  
The lower bound for the redshift range was empirically determined by the bright limit and the upper bound 
by the faint limit of the $M_{r}$ versus redshift distribution. 
The same fixed cumulative number density method, described above, is used on this SDSS EDP to equate
the cumulative number density of SDSS EDP to the highest redshift bin of the PRIMUS EDP. 
Ultimately, we get $M_{r,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$ for the redshift bins $0.06-0.145$, 
$0.2-0.4$, $0.4-0.6$, $0.6-0.8$, respectively.  %%%% PUT NEW VALUES
These absolute magnitude limits are illustrated in Figure \ref{fig:targetEDP}, which plots $M_{r}$ distribution as 
a function of redshift for the EDP (red) and the target galaxy sample (black).

@@

\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:smf}
        \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_25_primuszerr.eps,height=0.75\textwidth,angle=90}
        \caption{Evolution of the quiescent fraction for target galaxies in low (left) and (high) environments
from redshift range $z=0-0.8$. The QFs were calculated using the SMFs specificed in Figure \ref{fig:smf}. We use
lighter shades of orange for the QFs at higher redshifts.}
    \end{center}
\end{figure*}

@@

\section{Results}
In the section below, we calculate stellar mass functions (SMFs) for the target galaxy population divided into 
quiescent/star-forming and dense/sparse environment, Section \ref{sec:smf_const}. We use a non-parametric 
$1/V_{\rm{max}}$ estimate of SMFs for the subsamples further divided into redshift bins. Then using these 
SMFs, we calculate the quiescent fractions (QFs), Section \ref{sec:qf_const}, 
and examine it's evolution over our redshift range.

\subsection{Stellar Mass Function} \label{sec:smf_const}
The target galaxy sample defined above has so far
been classified into quiescent or star-forming and 
dense or sparse. We further divide these subsamples 
into bins of redshift:  in redshift bins of $0.06-0.145$, 
$0.2-0.4$, $0.4-0.6$, and $0.6-0.8$. While the 
PRIMUS data ranges from $0.2 < z < 1.2$, we only 
consider galaxies with $ z<0.8$ due to insufficient
statistics for robust environment measurements at 
higher redshifts. With added redshift bins, we have a
total of 16 subsamples. We calculate the SMF for 
each of these 16 subsamples.

@@

In order to calculate the uncertainty of the SMFs from the sample 
variance, we use a standard jackknife technique as done in \cite{Moustakas:2013aa}.
For the PRIMUS target galaxies, we calculate SMFs after excluding 
one of the five target fields each time. And for the SDSS target galaxies
we divide the field into a 30 $\times$ 20 rectangular $RA$ and $Dec$ 
grid and calculate the SMFs after excluding part of the field each time. 
Then using the calculated SMFs we calculate the uncertainty: 
\begin{equation}
\sigma^j = \sqrt{\frac{M-1}{M} \sum\limits_{k=1}^{M} (\Phi^j_k - \langle \Phi^j \rangle)^2}
\end{equation} 
$M$ in this equation is the number of jack knife SMFs in the stellar mass
bins. $\langle \Phi^j \rangle$ is the mean number density of galaxies 
in each stellar mass bin for all of the jack knife $\Phi^j$s. The SMFs for 
16 target galaxy subsamples classified into quiescent/star-forming (orange/blue)and 
dense/spare environments are presented in Figure \ref{fig:smf}. The 
redshift evolution of the SMFs are indicated by a darker shade for lower
redshifts. The sample variance uncertainties are represented by the 
width of the SMFs. The environment measurements and classifications
for Figure \ref{fig:smf} is done using a cylindrical aperture with dimensions,
$R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and $H_{\rm{ap}} = 25 \; \rm{Mpc}/h$.

Examining the SMF evolution over $z \sim 0 - 0.8$, we find that in dense 
environments, the quiescent SMFs increase by a factor of $over9000$ 
for $\mathcal{M}_{*} < 11.0$ while the SMF of the star-forming 
galaxies evolves little for all masses. Meanwhile in low density 
environments from $z=0.8$ to $0.0$, we find that the SMF of 
quiescent galaxies evolves little for all stellar masses and the 
SMF of star-forming galaxies decreases by a factor of $over9000$ 
for $\mathcal{M}_{*} > 10.5$.  
%%% EXPAND ON ANALYSIS OF SMF

\subsection{Quiescent Fraction} \label{sec:qf_const}
Using the SMF number densities ($\Phi$) calculated above, 
in this section, we compute the quiescent fraction, $f_{\rm{Q}}$ 
for dense and sparse environments over the redshift range 
$0.0 - 0.8$.  The quiescent fraction is simply given by the following 
equation: 
\begin{equation}
f_{\rm{Q}} = \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
\end{equation}
$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies 
per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.25$ 
for the quiescent and star-forming subsamples, respectively 
(Equation \ref{eq:phi}). The bottom panels of Figure \ref{fig:smf} 
shows the evolution of $f_{\rm{Q}}$ for dense (right) and sparse (left)
environments. As before, the darker shades of orange represent 
lower redshift bins.

%%% INCLUDE BRIEF QUALITATIVE ANALYSIS OF THE EVOLUTION OF THE QUIESCENT FRACTION

@@

The figures and analysis described in this paper are done using galaxy environment determined from a fixed aperture with $r_{\rm{ap}} = 1 \rm{Mpc}$ and $h_{\rm{ap}} = 50 \rm{Mpc}$.
The same analysis was repeated for various aperture dimensions: $r_{\rm{ap}} = 0.5, 1, 2, 3 \rm{Mpc}$ and $h_{\rm{ap}} = 25, 50 \rm{Mpc}$. 
Minor adjustments to the environment classification thresholds were adopted in these analyses for the smaller apertures ($r_{\rm{ap}} = 0.5, 1 \rm{Mpc}$ and $r_{\rm{ap}} = 25 \rm{Mpc}$).
The results obtained from using these different are consistent with the results displayed in this paper. 
\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_25_fidmass10_5_fixedslope_primuszerr.eps,height=0.5\textwidth}
        \label{fig:qf}
        \caption{Quiescent fraction at fiducial mass $\rm{log} (\mathcal{M}/\mathcal{M}_{\odot}) = 10.5$ for 
low (square) and high (circle) environments in the redshift range $z = 0 - 0.8$. The evolution of 
$f_{Q}(\mathcal{M}_{\rm{fid}})$ for galaxies in different environments shows an evolution over the redshift
range that is independent of environment density. Futhermore throughout the redshift range the difference in 
$f_{Q}(\mathcal{M}_{\rm{fid}})$ remains relatively constant and $ < 0.15$.}
    \end{center}
\end{figure}

\section{Discussion and Conclusions}
We have measured the SMFs and QFs using low redshift SDSS-{\em GALEX} galaxies and intermeidate redshift PRIMUS galaxies. 
Specifically we anlayzed the evolution of the QFs over the redshift range $0.0-1.0$ for galaxies in environment densities (Figure \ref{fig:qf}). 
We find that there is an expected increase in QF with decrease in the redshift for subsamples in all environment densities.
More importantly we find that the change in QF over redshift is independent of the environment and remains relatively equal for all environments.

@@

\subsection{Stellar Mass Function} \label{sec:smf_const}
\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:smf}
        \epsscale{1.0}
        \plotone{fig_smf_cylr1h25_thresh80_bin0_25.png}
        \caption{SMF for $r_{\rm{ap}}=1 \rm{Mpc}$ and $h_{\rm{ap}}=25 \rm{Mpc}$}
    \end{center}
\end{figure*}

\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:smf}
        \epsscale{1.0}
        \plotone{fig_qf_cylr1h25_thresh80_bin0_25.png}
        \caption{QF for $r_{\rm{ap}}=1 \rm{Mpc}$ and $h_{\rm{ap}}=25 \rm{Mpc}$}
    \end{center}
\end{figure*}

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \plotone{fig_qffit_cylr1h25_thresh80_bin0_25.png}
        \label{fig:qf}
        \caption{QF at fiducial mass for $r_{\rm{ap}}=2 \rm{Mpc}$ and $h_{\rm{ap}}=50 \rm{Mpc}$}
    \end{center}
\end{figure*}
